Learning to Infer Graphics Programs from Hand-Drawn Images

### 2017-05-19 paper.tex
very close page limit

The second step involves generating a high-level program capable of producing the program trace identified by the first phase. In principle, we could also train a neural network to learn this mapping. In practice, though, this would be challenging because it would no longer be sufficient to train the network with a synthetic corpus of randomly generated programs, since our goal is to generate programs that satisfy certain semantic constraints that ensure that we get the program that the user most likely intended. This paper argues that this stage is best achieved by \emph{constraint-based program synthesis} \cite{}. Without the need for training, the program synthesizer can search the space of possible programs for one capable of producing the desired trace under a quantitative objective that maximizes the likelihood according to a prior distribution that aims to capture the user’s preference.

@@

There are many directions for future work. In the parsing phase, the proposal network currently samples positional variables on a discrete grid. More general types of drawings could be supported by instead sampling from continuous distributions, e.g. using Mixture Density Networks~\cite{MDN}. The proposal network also currently handles only a very small subset of \LaTeX drawing commands, though there is no reason that it could not be extended to handle more with a higher-capacity network. Exploring more sophisticated network architectures, including ones that utilize attention~\cite{mnih2014recurrent}, could also help correct some of the errors the network makes.
In the synthesis phase, a more expressive DSL---including subroutines, recursion, and symmetry groups beyond reflections---would allow the system to effectively model a wider variety of graphical phenomena. The synthesizer itself could also be the subject of future work: the system currently uses the general-purpose Sketch synthesizer, which can take minutes to hours to run, whereas program synthesizers which are custom-built for special problem domains can run much faster or even interactively~\cite{le2014flashextract}.

In the not-too-distant future, we believe it should be possible to produce professional-looking figures just by drawing them and then letting an artificially-intelligent agent write the corresponding code.
More generally, we believe that the two-phase system we have proposed---parsing into execution traces, then searching for a low-cost symbolic program which generates those traces---may be a useful paradigm for other domains in which agents must programmatically reason about noisy perceptual input.

>>>>

The second step involves generating a high-level program capable of producing the program trace identified by the first phase.
%In principle, we could also train a neural network to learn this mapping. In practice, though, this would be challenging because it would no longer be sufficient to train the network with a synthetic corpus of randomly generated programs, since our goal is to generate programs that satisfy certain semantic constraints that ensure that we get the program that the user most likely intended.
This paper argues that this stage is best achieved by \emph{constraint-based program synthesis} \cite{solar2008program}. Without the need for training, the program synthesizer can search the space of possible programs for one capable of producing the desired trace.
%under a quantitative objective that maximizes the likelihood according to a prior distribution that aims to capture the user’s preference.

@@

There are many directions for future work. In the parsing phase, the proposal network currently samples positional variables on a discrete grid. More general types of drawings could be supported by instead sampling from continuous distributions, e.g. using Mixture Density Networks~\cite{MDN}. The proposal network also currently handles only a very small subset of \LaTeX drawing commands, though there is no reason that it could not be extended to handle more with a higher-capacity network. Exploring more sophisticated network architectures, including ones that utilize attention~\cite{mnih2014recurrent}, could help correct some of the errors the network makes.
In the synthesis phase, a more expressive DSL---including subroutines, recursion, and symmetry groups beyond reflections---would allow the system to effectively model a wider variety of graphical phenomena. The synthesizer itself could also be the subject of future work: the system currently uses the general-purpose Sketch synthesizer, which can take minutes to hours to run, whereas program synthesizers which are custom-built for special problem domains can run much faster or even interactively~\cite{le2014flashextract}.

In the not-too-distant future, we believe it should be possible to produce professional-looking figures just by drawing them and then letting an artificially-intelligent agent write the code.
More generally, we believe that the two-phase system we have proposed---parsing into execution traces, then searching for a low-cost symbolic program which generates those traces---may be a useful paradigm for domains in which agents must programmatically reason about noisy perceptual input.
